Reading source files and preparing data sets

### 2024-11-05 data-raw/01-preprocessing-source-files.Rmd
updating episode and impedance data

```{r creating an integrated data}
# creating an integrated data frame from 1986 to 2015
gss_episodes <- rbind(walking_2015, cycling_2015, walking_2010, cycling_2010, walking_2005, cycling_2005, cycling_1998, walking_1998, walking_1992, cycling_1992, walking_1986)

# Change the name of some values in the dest column in the dataset 
# Ensure that 'dest_label' is the correct column name
gss_episodes <- gss_episodes |>
  mutate(dest_label = case_when(
    dest_label == "Restaurant/bar" ~ "Restaurant, bar or club",
    dest_label == "Outdoors away from home" ~ "Outdoors",
    dest_label == "Grocery store, other stores or mall" ~ "Grocery store",
    dest_label == "Restaurant, bar or club" ~ "Restaurant",
    dest_label == "Sports centre, field or arena" ~ "Sport area",
    dest_label == "Medical, dental or other health clinic" ~ "Health clinic",
    dest_label == "In the neighbourhood" ~ "Outdoors",
    dest_label == "Library, museum or theatre" ~ "Library",
    TRUE ~ dest_label  # This line ensures other values remain unchanged
  ))
```

>>>>

```{r creating an integrated data}
# creating an integrated data frame from 1986 to 2015
gss_episodes <- rbind(walking_2015, cycling_2015, walking_2010, cycling_2010, walking_2005, cycling_2005, cycling_1998, walking_1998, walking_1992, cycling_1992, walking_1986)
```
